### 2014-01-14 src/paper.Rnw
update

Research in software testing often involves comparison between different testing techniques.
\Mua originally proposed by Lipton \cite{lipton1971fault} involves systematic transformation of program through introduction of first order syntactical changes.
The ability of test suites to distinguish the variants -- mutation score -- thus produced is taken as the effectiveness of the test suite\cite{ammann2008introduction}, and is used as an indicator for the effectiveness of the test suite against real faults\cite{andrews2005mutation}.

\Mua relies on two main assumptions: competant programmer hypothesis, and coupling effect\cite{budd1979mutation}.
Competant programmer hypothesis suggests that the version of program produced by a competant programmar is close to the final version,
while coupling effect claims that a test suite capable of catching first order bugs will also detect higher order bugs that contain these first order bugs.

For \mua to be used as a successful tool for comparison of testing techniques, the mutants produced by \mua should be similar in charecteristics to the real faults found in software.
This was investigated by Andrews et al.\cite{andrews2005mutation}, where it was found in one of the programs under consideration `space.c' for which real faults were available, the ease of detecting mutants was very close to the ease of detecting real faults.
However, for the other programs under consideration from siemens suite, the faults seeded by hand were much more harder to detect than mutants.
From this, Andrews et al. concluded that mutants produced were similar in characteristic to the real faults in terms of ease of detection.
However, this has come under attack for various reasons.
For example, the analysis depended on a single program which may not be a good representative of the other programs.
Further, Namin et al.\cite{namin2011theuse} found that different factors such as different programming languages, test suite size, and mutation operators chosen has an impact on whether the mutants produced are similar to real faults in terms of ease of detection.

This has led us to investigate real faults in software in a larger scale, especially paying attention to programming langauges of four different kinds: C, Java, Python and Haskell.
We have used the revision control histories of open source projects as obtained from Github\cite{github}. From these, we have identified changes that correspond to bugfixes using machine learning techniques. We have also identified the changes that are simple.

This research makes the following contributions.

\begin{enumerate}
\item contrib
\end{enumerate}

>>>>

Mutation analysis originally proposed by Lipton\cite{lipton1971fault} involves systematic transformation of program through introduction of first order syntactical changes\cite{ammann2008introduction}. Researchers have shown that the mutations thus introduced behave similarly to the real faults\cite{andrews2005mutation}, and hence can be used as a stand-in for real faults when determining the efficacy of a test suite against faults.

While mutation analysis provides a useful metric, its use has been held back due to its high computational requirements\cite{jia2011analysis}. This has led researchers to search for ways of reducing the resource requirements of the analysis.
The methods in this direction can be classified into ``Do faster'', ``Do fewer'', and ``Do smarter''\cite{offutt2001mutation}. The ``Do fewer'' approach has come in for special study, and various researchers have investigated different ways to reduce the number of mutants thus produced.

One of the main approaches is selective mutation, proposed by Mathur\cite{mathur1991performance}, and further refined by Offutt et al.\cite{offutt1993anexperimental}. This approach relies on the fact that some of the mutagens generate a large number of variants, and hence produce highly redundant test cases. Previous research suggested that elimination of mutagens with high fertility results in the reduction of total number of mutations produced, and hence reduces the computational requirements.

% TODO check the survey again on selective mutation.

It was recently questioned whether this approach indeed resulted in a tangible improvement over random selection of mutants\cite{zhang2010operator}, which did not find operator based selection to be better than random selection. It was later found that using operator based selection and random sampling was better than using each strategy separately\cite{zhang2013ase}.

Another research, initially by Unch\cite{untch2009onreduced} and recently by Deng et al.\cite{deng2013empirical} suggests using software deletion operator since it produces the least number of mutants (smallest neighborhood). The researchers were able to obtain a close approximation of original mutant score with significant savings with this approach.

However, our previous research\cite{icse} suggests that mutation coverage is closely predicted by statement coverage, this suggests that any criteria that forces accounting of the impact of each statement should provide a close approximation to the full mutation score. Hence, our research suggests that SDL works because it forces accounting of each line, and a random sampling criteria that provides the same criteria should result in similar results.

In our analysis, we find that a random sampling approach that randomly chose a single mutant per line was found to have a better correlation with the full mutation score than that obtained by SDL. Further it was also found that the mutation score produced by random sampling was closer to the full mutation score than that produced by SDL.
